Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-08-29 Manuscript.Rmd
Adding images to results

---
title: "Parsing mPFC: Community analysis"
author: "Claudio Toro-Serey & Joseph T. McGuire"
#date: "7/2/2018"
output:
  html_document: default
  pdf_document: default
---

@@

## Introduction
  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

@@

**Meta-analysis**
We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each peak volumetric coordinate, 10mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer. The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016). This produced a list of standardized parcels that were reported on each study.

@@

Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which include considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152 normalization, all scans went through a number of additional refinements (Tobyne et al., 2017). Only subjects with both left-right and right-left phase encoding were included. In addition, only datasets with either low motion levels (under 1.5mm) or 0.5mm mean framewise displacement (FD) were used. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR). Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject. Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day).

**Within-ROI Connectivity**
To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,942 per subject) and computed the Pearson correlation of the time series of every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we took the exponential of the correlations, Fisher transformed them (i.e. tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).

For the main goal of this section, I maximized the strength-based modularity metric as a community detection method (fast-greedy algorithm), so that I could check if all the DMN ROIs from the previous section were affiliated with the same community. While this measure has resolution problems at large and low scales (Fortunato & Hric, 2016), if it does extract a close match to standard DMN networks, it could act as a good method for the final stage of the project (but see Peel, Larremore, and Clauset 2017 for issues with ground-truth). Even though this analysis is mainly geared to confirm that these ROIs are jointly captured, this step also let me examine whether some of the ROIs could be subdivided into DMN and non-DMN regions at this level of granularity.

In order to evaluate the validity of the modularity-based communities, I also clustered the brain by means of spectral partitioning. Specifically, I took the Fiedler vector (eigenvector associated with the second lowest eigenvalue) from each participant’s normalized Laplacian matrix, and divided the brain by the sign of the eigenvector values. This analysis served the additional purpose of more strictly dividing the brain into DMN and non-DMN communities. Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016). Finally, to quantify the agreement of these community methods, I computed both the adjusted rand index and variation of information distance (normalized by the logarithm of the number of vertices, 360 in this case) between them per subject. The adjusted rand index denotes the proportion of vertices that coincide in affiliation across partitions, and compares this score to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions. While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case. Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016). Importantly, due to having just 3 subjects, I abstained from performing formal statistics on the descriptive measures that I show.

For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two. That means that the vertices became smaller functional brain units that are connected by the same type of edge (i.e. adjusted correlations) as in step two. This time, I only focused on partitioning the brain through modularity and spectral partitioning to see if the ROIs can be subdivided at this finer level of resolution. It is worth noting that while communities across subjects should be similar, the idiosyncrasies explained previously (i.e. cortical folding) should produce noticeable differences as well.

This time I added two new areas to the ROIs: 7m, as this area had unique relevance in DMN when compared to valuation (evidenced by its connectivity strength in DMN and chi- squared permutation in the meta-analysis, see results), and V1, as this visual processing area should not be affiliated with DMN. These regions thus acted as dual reference points, such that the community affiliated with 7m should denote DMN, while V1 indicated non-DMN. As before, I tested the validity of the partitions using the adjusted rand index and normalized variation of information. However, this time I also used the rand index to quantify the community correspondence between subjects. Specifically, I divided each subject’s spectrally- partitioned brain into PCC and mPFC topographical zones (posterior and frontal brain, respectively), and computed the index of each region between subjects. The high cross-subject heterogeneity of cortical folding of mPFC should produce relatively low rand indices, while the more homogeneous PCC should display the opposite pattern. This analysis was meant to tackle the subject-specific limitations discussed above. The final patterns were inspected visually.

@@

**Evaluation**

## Results
## Partition Comparison: Full Datasets

Just as reference, the following shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.

``` {r Partition comparison: all brain example, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first=1, last=6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)

plotCommunities(Summaries[[1]], Hemi = "L", Legends = F, type = "FiedlerBinary")

@@

``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
# Cross-method
# Don't worry about plotting, since that's mainly for a general visualization
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)

@@

``` {r Partition comparison: all 2, fig.align="center", echo=FALSE, message = FALSE}
# Across subjects
# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "b")
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         cl.pos = "n", 
         add = T)

@@

``` {r Partition comparison: halves, fig.align="center", echo=FALSE, message = FALSE}
# Select 10 subjects from the sample to display
selectSubj <- seq(1,20)

@@

``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
# Now compare all possible pairs of subjects
# Compare all halves with RI
RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)

@@

``` {r Partition comparison: session similarity matrices, fig.align="center", echo=FALSE, message = FALSE}
# Select 10 subjects from the sample to display
selectSubj <- seq(1,40)

@@

``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
## Brain storming:
## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
## Perhaps a more interresting idea would be to generate an index of variance within/between subject
## These are just attempts at that are not perfect:

@@

``` {r Partition comparison: session linear model, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
# 2) Based on Kragel et al, 2018
# First, create a disimilarity matrix
dissimMatrix_all <- RI_all_between_sess
dissimMatrix_lower <- dissimMatrix_all[lower.tri(dissimMatrix_all)]

@@

``` {r Stability per subject: Overall, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE}
# Load files
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

@@

``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE}
## Check stability for PCC and mPFC separately
# Get the sliding values for PCC and PFC separately
tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)

@@

``` {r Stability per subject: SNR Comparison, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

@@

``` {r Stability per subject 4, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE}
setwd('./Variance/')
temp <- list.files()
Variance <- lapply(temp, read.csv)

@@

``` {r Stability per subject 6, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE}
# grid.arrange(v6, v7, ncol = 2)
par(mfrow = c(1,2))
smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
              xlab = "R-squared Value",
              ylab = "Z-Coordinate")

@@

``` {r Correlation vs community detection: plot, fig.align="center", echo=FALSE, message = FALSE}
## Between halves analysis for correlation and communities (mPFC only)
tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- tempComm_PFC_halves_plot
D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
corrplot(allHalfCombs, 
         title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.6,
         cl.pos = "b",
         mar = c(0,0,3,0))
segments(0.5,0.5,0.5,40.5, lwd = 2)
segments(0.5,0.5,40.5,0.5, lwd = 2)
segments(0.5,40.5,40.5,40.5, lwd = 2)
segments(40.5,0.5,40.5,40.5, lwd = 2)
segments(0.5,20.5,40.5,20.5, lwd = 2)
segments(20.5,0.5,20.5,40.5, lwd = 2)

@@

``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE}
# Compare correlation with community approach on mPFC
# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
# prepostComp <- melt(prepostComp)
# colnames(prepostComp) <- c("Approach", "Correlation")
# prepostComp_test <- permute(tempComm, tempCor, paired = T)
# 
# 
# ## Between halves analysis for correlation and communities (mPFC only)
# D1 <- tempComm_PFC_halves
# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
# Data <- c(D1,D2)
# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
#

@@

Finally, we examined whether these topological features were defined by the structure of the brain by correlating each subject's Fiedler vector with their structural MRI data. We found that the Fiedler vector is uncorrelated with myelin density (mean correlation = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean correlation = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean correlation = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`). While these results suggest that each subject's functional topology is mostly independent of brain structure, we will perform more detailed analyses of this in the future (i.e. are there any outstanding structural features in a subject that match their unique topology?).  
## Discussion
For clinical implications, see Hiser & Koenigs 2018. In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC. It would be more interesting to identify the repercussions to damage in mPFC per individual. They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment. The refinement of the technique is thus coupled to being able to identify personalized functional topologies. They list a number of results related to mPFC functional connectivity too. In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse. (note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)

>>>>

---
title: "Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach"
author: "Claudio Toro-Serey & Joseph T. McGuire"
#date: "7/2/2018"
output:
  pdf_document: default
  html_document: default
---

@@

## Introduction

  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

@@

**Meta-analysis**
We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer. The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016). This produced a list of standardized parcels that were reported on each study.

@@

Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements (Tobyne et al., 2017). These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression (MGSR; Burgess et al., 2016). Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

**Within-ROI Network Definition**
To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,564 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we took the exponential of the correlations, Fisher transformed them (i.e. tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately; 2) the concatenated timeseries from each pair of daily sessions; 3) each subject's dataset; and 4) on each step of a sliding window analysis (see Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975). First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,564). This matrix was then transformed into its normalized Laplacian form

$$\begin{aligned}
L = I - D^{-\frac{1}{2}}AD^{-\frac{1}{2}}
\end{aligned}$$

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and $A$ is the correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected (Fiedler, 1975). Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis. Importantly, given the high density of these networks (**Add to results**), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).

In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization (using the algorithm from Clauset et al., XXXX). This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity. Thus, unlike SP, modularity can subdivide a network into many functional groups. If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

**Partition Evaluation**
To quantify the agreement between partitions, we computed both the adjusted rand index and variation of information distance. The adjusted rand index denotes the proportion of vertices that coincide in affiliation across partitions, and compares this score to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions. While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case. Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).

 However, this time I also used the rand index to quantify the community correspondence between subjects. Specifically, I divided each subject’s spectrally- partitioned brain into PCC and mPFC topographical zones (posterior and frontal brain, respectively), and computed the index of each region between subjects. The high cross-subject heterogeneity of cortical folding of mPFC should produce relatively low rand indices, while the more homogeneous PCC should display the opposite pattern. This analysis was meant to tackle the subject-specific limitations discussed above. The final patterns were inspected visually.

## Results
## Meta-analysis

Figure 1 shows the resulting ROIs from the meta-analysis. Areas in blue denote the 17 overlapping ROIs, which landed mostly on the medial wall, as well as a region in IPL and TPJ. Area 7m (in red) was the only one to show unique affiliation, which was significant for DMN.

```{r Meta-analysis ROIs, out.width="60%", out.height="40%", fig.align = "center"}
include_graphics("ROIS.png")
```

## Partition Comparison: Full Datasets

The following shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.

```{r Template partition, out.width="60%", out.height="40%", fig.align = "center"}
include_graphics("template.png")
```

@@

``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
# Cross-method
# Don't worry about plotting, since that's mainly for a general visualization
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)

@@

``` {r Partition comparison: all 2, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
# Across subjects
# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "b")
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         cl.pos = "n", 
         add = T)

@@

``` {r Partition comparison: halves, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
# Select 10 subjects from the sample to display
selectSubj <- seq(1,20)

@@

``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
# Now compare all possible pairs of subjects
# Compare all halves with RI
RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)

@@

``` {r Partition comparison: session similarity matrices, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
# Select 10 subjects from the sample to display
selectSubj <- seq(1,40)

@@

``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
## Brain storming:
## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
## Perhaps a more interresting idea would be to generate an index of variance within/between subject
## These are just attempts at that are not perfect:

@@

``` {r Partition comparison: session linear model, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
# 2) Based on Kragel et al, 2018
# First, create a disimilarity matrix
dissimMatrix_all <- RI_all_between_sess
dissimMatrix_lower <- dissimMatrix_all[lower.tri(dissimMatrix_all)]

@@

``` {r Stability per subject: Overall, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
# Load files
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

@@

``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
## Check stability for PCC and mPFC separately
# Get the sliding values for PCC and PFC separately
tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)

@@

``` {r Stability per subject: SNR Comparison, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

@@

``` {r Stability per subject 4, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
setwd('./Variance/')
temp <- list.files()
Variance <- lapply(temp, read.csv)

@@

``` {r Stability per subject 6, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
# grid.arrange(v6, v7, ncol = 2)
par(mfrow = c(1,2))
smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
              xlab = "R-squared Value",
              ylab = "Z-Coordinate")

@@

``` {r Correlation vs community detection: plot, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- tempComm_PFC_halves_plot
D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
corrplot(allHalfCombs, 
         title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.6,
         cl.pos = "b",
         mar = c(0,0,3,0))
segments(0.5,0.5,0.5,40.5, lwd = 2)
segments(0.5,0.5,40.5,0.5, lwd = 2)
segments(0.5,40.5,40.5,40.5, lwd = 2)
segments(40.5,0.5,40.5,40.5, lwd = 2)
segments(0.5,20.5,40.5,20.5, lwd = 2)
segments(20.5,0.5,20.5,40.5, lwd = 2)

@@

``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
# Compare correlation with community approach on mPFC
# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
# prepostComp <- melt(prepostComp)
# colnames(prepostComp) <- c("Approach", "Correlation")
# prepostComp_test <- permute(tempComm, tempCor, paired = T)
# 
# 
# ## Between halves analysis for correlation and communities (mPFC only)
# D1 <- tempComm_PFC_halves
# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
# Data <- c(D1,D2)
# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
#

@@

Finally, we examined whether these topological features were defined by the structure of the brain by correlating each subject's Fiedler vector with their structural MRI data. We found that the Fiedler vector is uncorrelated with myelin density (mean correlation = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean correlation = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean correlation = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`). While these results suggest that each subject's functional topology is mostly independent of brain structure, we will perform more detailed analyses of this in the future (i.e. are there any outstanding structural features in a subject that match their unique topology?).

## Discussion

For clinical implications, see Hiser & Koenigs 2018. In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC. It would be more interesting to identify the repercussions to damage in mPFC per individual. They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment. The refinement of the technique is thus coupled to being able to identify personalized functional topologies. They list a number of results related to mPFC functional connectivity too. In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse. (note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
